IPv6 over Low-Power Wireless Personal Area Networks\\ MSc. Thesis Proposal

### 2009-12-01 trunk/doc/msc-proposal/msc-proposal.tex
propsal: adaptation layer

%\department{Department of Electrical Engineering and Computer Science}

@@

\newpage
\tableofcontents
%\listoffigures 
\newpage

@@

\section{Adaptation layer}\label{sec:adapt.layer}
The IPv6 minimum Maximum Transmission Unit (MTU) size is defined as 1280 octets. As described in Chapter \ref{ch:ieee802.15.4}, the maximum IEEE 802.15.4 frame size is limited to 127 octets.  Taking into account the maximum frame overhead of 25 octets, 102 octets are left at the media access control layer. Link-layer security imposes further overhead, which in the maximum case (21 octets for AES-CCM-128) leaves only 81 octets available, which is far below the minimum IPv6 packet size. Therefor, a fragmentation and reassembly adaptation layer is provided at the layer below IP.

IPv6 datagrams transported over IEEE 802.15.4 are prefixed by an encapsulation header stack. Each header in the header stack contains a header type followed by zero or more header fields.  Three optional encapsulation headers may appear in the following order: Mesh Addressing Header, Broadcast Header and Fragmentation Header. These headers are described in Sections \ref{subsec:mesh.header}, \ref{subsec:frag.header} and \ref{subsec:broad.header} respectively. The Dispatch

\subsection{Fragmentation Header}\label{subsec:frag.header}
\subsection{Mesh addressing Header}\label{subsec:mesh.header}
\subsection{Broadcast Header}\label{subsec:broad.header}

>>>>

\newenvironment{mylisting}
{\begin{list}{}{\setlength{\leftmargin}{1em}}\item\footnotesize}
{\end{list}}

\newenvironment{mytinylisting}
{\begin{list}{}{\setlength{\leftmargin}{1em}}\item\tiny\bfseries}
{\end{list}}

@@

\newpage
\tableofcontents
\listoffigures 
\newpage

@@

\section{Adaptation layer}\label{sec:adapt.layer}
The IPv6 minimum Maximum Transmission Unit (MTU) size is defined as 1280 octets. As described in Chapter \ref{ch:ieee802.15.4}, the maximum IEEE 802.15.4 frame size is limited to 127 octets.  Taking into account the maximum frame overhead of 25 octets, 102 octets are left at the media access control layer. Link-layer security imposes further overhead, which in the maximfum case (21 octets for AES-CCM-128) leaves only 81 octets available, which is far below the minimum IPv6 packet size. Therefor, a fragmentation and reassembly adaptation layer is provided at the layer below IP.

IPv6 datagrams transported over IEEE 802.15.4 are prefixed by an encapsulation header stack. Each header in the header stack contains a header type followed by zero or more header fields.  There are four encapsulation headers defined: Mesh Addressing Header, Broadcast Header and Fragmentation Header (described in Sections \ref{subsec:mesh.header}, \ref{subsec:frag.header},\ref{subsec:broad.header} and \ref{subsec:dispatch.header} respectively). The headers must appear in the specified order. First three of them are optional, whereas the last one is required.

\subsection{Dispatch Header}\label{subsec:dispatch.header}
The dispatch type is defined as a zero bit as the first bit followed by a one bit.

\begin{figure}[htp]
\centering
\begin{mylisting}
\begin{verbatim}
                     1                   2                   3
   0 1 2 3 4 5 6 7 8 9 0 1 2 3 4 5 6 7 8 9 0 1 2 3 4 5 6 7 8 9 0 1
  +-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
  |0 1| Dispatch  |  type-specific header
  +-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
\end{verbatim}
\end{mylisting}
\caption{Dispatch Type and Header}\label{fig:dispatch.header}
\end{figure}
The Dispatch value identifies the type of header immediately following the Dispatch Header.

\subsection{Mesh addressing Header}\label{subsec:mesh.header}
\subsection{Fragmentation Header}\label{subsec:frag.header}
\subsection{Broadcast Header}\label{subsec:broad.header}
